Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
Update paper.tex

Auto-tuning techniques attempt to find a good solution among a huge space of
available system configurations. However, in practice auto-tuning is limited
to only the configuration tunables that the storage system exposes and can be
overwhelmed with too many parameters.  For instance, auto-tuning may be
capable of identifying instances in which new data layouts would benefit a
workload, but unless the system can provide such a transformation, the option
is left off the table.  Starfish~\cite{herodotou:cidr2011-starfish} made
an attempt of this for Hadoop but this technique would need to severely limit
the space of parameters in order to feasible, similar to the approach used in~\cite{behzad:sc2013-autotuning}.

>>>>

Auto-tuning techniques attempt to find a good solution among a huge space of
available system configurations. However, in practice auto-tuning is limited
to only the configuration tunables that the storage system exposes and can be
overwhelmed with too many parameters.  For instance, auto-tuning may be
capable of identifying instances in which new data layouts would benefit a
workload, but unless the system can provide such a transformation, the option
is left off the table.  Starfish~\cite{herodotou:cidr2011-starfish} made
an attempt at this for Hadoop but this technique would need to severely limit
the space of parameters in order to be feasible, similar to the approach used in~\cite{behzad:sc2013-autotuning}.
